%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {M.ENG (Hons), Engineering, 4th Year Student} % Degree
    {University of Cambridge} % Institution
    {Cambridge, United Kingdom} % Location
    {Oct. 2018 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {First Year: High 2.i (74\%) ; Second Year: Ungraded (As a result of CoVid-19) ; Third Year: High 2.i (71\%).}
        \item {Specialised in \textbf{Information and Computer Engineering and Bioengineering}.}
        \item {\textbf{4th year Papers}: Machine Learning, Deep Learning, Computer Vision, Robotics, Information Theory, Computational Neuroscience, Bioelectronics, Software Engineering Principles.}
        \item {\textbf{3rd year Papers}: Signals and Systems, Signal Processing, Information Theory, Inference, 3D Computer Imaging, Molecular Bioengineering, Neuroscience, Mathematics, Marketing, Economics, French.}
        \item {\textbf{Masters NLP Research Project}: Project involved using natural language processing and machine learning to train a counter speech dialogue system that can respond intuitively to hate speech. Introduced a custom unsupervised evaluation metric using neural networks with associated custom data sets. Fine tuning of state-of-the-art dialogue systems such as BlenderBot was done to create a convincing dialogue system.}
        \item {\textbf{Multidisciplinary Design Project}: Innovated a way of aggregating metrics in hospitals and care home wards with environmental monitoring systems to distribute a compact live data monitoring system to nurses and other care staff. Established a serial connection between Arduino sensors and a Raspberry Pi, this data was fed into the L2S2 system via Xenplate API to be displayed.}
        \item {\textbf{Integrated Design Project}: Led the full construction of a minesweeping robot made to detect and move magnetic blocks. Worked primarily on the software side of the project in writing code for the sensors and motor controls in C++. Worked using Arduino environment, interfaced using Wi-Fi to a backend python script running computer vision (OpenCV) algorithms.}
        \item {\textbf{Machine Learning Self Project}: Built and trained a fully convolutional neural network for image segmentation in PyTorch with Python using standard network architecture involving convolutional and ReLu layers (u-net style). Trained network using training images and plotted associated training loss. Code was used to analyse satellite images and segment the image into man made buildings and natural landscapes. Network could achieve 80\%+ accuracy on minimal training data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {High School} % Degree
    {Westlake Boys High School} % Institution
    {Auckland, New Zealand} % Location
    {Feb. 2013 - Dec. 2017} % Date(s) 
    {
      \begin{cvitems}
        \item {\textbf{A Levels}: Mathematics (A*), Physics (A*), Chemistry (A*), Biology (A*), English Literature (A*)}
        \item {\textbf{NZQA Scholarships}: Outstanding Scholarships in Chemistry and Statistics, Scholarships in Physics, Calculus, Earth and Space Science, Biology and English}
      \end{cvitems}
    }
\end{cventries}
