%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Cambridge University Robotics Society} % Organization/group
    {Cambridge, United Kingdom} % Location
    {Nov. 2018 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed a behavioural and vision system for robots to compete in a football tournament. This involved building out a computer vision framework for the robot implemented using OpenCV in python.}
        \item {Designed an optimisation strategy using image pre-processing to increase computational efficiency that reduced computation times by over 100\%.}
        \item {Collaborated on a behavioural system that optimized the path planning system when the robot is moving into positions. This was computed using trajectory planning and Bezier curves in C++.}
        \item {Developed an audio transmission system for the robot rescue major which integrated front-end JavaScript with ROS audio to create a web-based system that could send and receive audio.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {Cambridge University Spaceflight Society} % Organization/group
    {Cambridge, United Kingdom} % Location
    {Oct. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Role in developing the core segment of rocket connecting oxidizer tank and oxidizer i.e., fuel injection mechanism and complementary ground support systems.}
        \item {CAD development (Solidworks), 3D printing, laser cutting and machining of parts including oxidizer fuelling line disconnection system and post launch sealing mechanism.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
